SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Small changes

It allows to define higher-order systems
by assigning an initial condition to a `Derivative`:

@@

    p: Parameter = assign(default=1)
    z: Variable = initial(default=p)  # typing error
```

>>>>

It also allows to define higher-order systems
by assigning an initial condition to a `Derivative`:

@@

    p: Parameter = assign(default=1)
    z: Variable = initial(default=p)  # type error
```
